---
title: 'Crop data'
output: html_document
editor_options: 
  chunk_output_type: console
---

## Packages

```{r packages}
require(data.table)
require(sf)
require(mapview)
require(stringr)
require(plyr)
require(dplyr)
require(ggplot2)
require(forcats)
require(tidyr)
require(tmap)
require(tmaptools)
require(grid)
require(gridExtra)
require(RColorBrewer)
require(shiny)
require(shinyjs)
```

## Harvest data

```{r data-harvest}
# read list of files
fl_vec = list.files('data/nrw', pattern = 'csv', full.names = TRUE)
l = list()
for (i in seq_along(fl_vec)) {
  fl = fl_vec[i]
  dat = fread(fl, skip = 7, header = TRUE, encoding = 'Latin-1', stringsAsFactors = FALSE)
  dat = dat[-1, ]
  setnames(dat, 1:2, c('rs', 'gen'))
  
  l[[i]] = dat
  names(l)[i] = gsub('ernte|.csv', '', basename(fl))
}
# bind list of data.table to one data.table
dt = rbindlist(l, fill = TRUE, idcol = 'year')
# remove special symbols and convert column types to numeric
cols = names(dt)[ ! names(dt) %in% c('year', 'rs', 'gen')]
dt[ , (cols) := lapply(.SD, function(x) gsub('\\.|-', NA, x)),
    .SDcols = cols ]
dt[ , (cols) := lapply(.SD, function(x) gsub(',', '.', x)),
    .SDcol = cols ]
dt = dt %>%
  mutate_at(c(4:41), ~as.numeric(.)) %>%
  mutate_at(c(4:41), ~replace(.,is.na(.),0))
# bring data into long format (year, rs, gen as identifier variables)
crop_names = colnames(dt[,4:41])
setDT(dt)
dt_long = melt(dt, id.vars = c('year','rs','gen'), measure.vars = crop_names, variable.name = 'crop', value.name = 'dtha' )
```

```{r data-spatial-regions}
kreis = st_read(file.path('data', 'germany_kreis.shp'), stringsAsFactors = FALSE)
setnames(kreis, tolower(names(kreis)))
kreis$rs = as.numeric(kreis$rs)
kreis2 = kreis[ , names(kreis) %in% c('rs', 'rs_alt', 'geom', 'shape_leng', 'shape_area') ]
# refine to NRW only
nrw <- kreis2 %>% 
  filter(substr(rs_alt,1,2) == "05")
#nrw as a whole geometry for visualization purposes
nrw_full = st_union(st_geometry(nrw))
```
According to the german district number, formally called 'Amtlicher Gemeindeschlüssel' and referenced by rs_alt, the first to digits '05' indicate the federal state 'North Rhine-Westphalia'.

To organize the data, the crops were renamed and categorized in another column into 12 factors.
```{r merge and categorize}
# merge geo and crop data
fin = merge(nrw, dt_long)
# shorten crop names
cropnms = gsub('[.]', ' ', crop_names)
cropnms[1] = 'GetreidemitCCM'
cropnms[2] = 'GetreideohneCCM'
cropnms[7] = 'Hartweizen'
cropnms[8] = 'RoggenmitWG'
cropnms[11] = 'Futtergetreide'
cropnms[10] = 'Wintergetreide'
cropnms[16] = 'Sommergetreide'
cropnms[18] = 'KörnermaismitCCM'
cropnms[21] = 'Spätkartoffeln'
cropnms[24] = 'Leguminosen'
cropnms[25] = 'Erbsen'
cropnms[28] = 'Sommerraps'
cropnms[31] = 'Getreideganz'
cropnms[33] = 'Weiden'
cropnms[34] = 'Feldgras'
cropnms[35] = 'KleeLuzerne'
cropnms[37] = 'Silomais'
# rename crops
fin$crop = mapvalues(fin$crop, from = crop_names, to = cropnms)
# categorize crops
fin = fin %>%
  mutate(cropcat = case_when(crop %in% c('GetreidemitCCM','GetreideohneCCM','Brotgetreidearten','Wintergetreide','Futtergetreide','Sommergetreide','Triticale') ~ 'cereal',
        crop %in% c('Winterweizen','Sommerweizen','Getreideganz','Hartweizen','Weizen') ~ 'wheat',
        crop %in% c('RoggenmitWG','Roggen') ~ 'rye',
        crop %in% c('Gerste','Wintergerste','Sommergerste') ~ 'barley',
        crop %in% c('Hafer') ~ 'oat',
        crop %in% c('KörnermaismitCCM','Silomais') ~ 'maize',
        crop %in% c('Frühkartoffeln','Kartoffeln','Spätkartoffeln') ~ 'potatoes',
        crop %in% c('Zuckerrüben','Runkelrüben') ~ 'beets',
        crop %in% c('Winterraps','Sommerraps') ~ 'rapeseed',
        crop %in% c('Sonnenblumen') ~ 'sunflower',
        crop %in% c('Leguminosen','Erbsen','Ackerbohnen','KleeLuzerne','Luzerne','Süßlupinen') ~ 'legumes',
        crop %in% c('Wiesen','Weiden','Feldgras','Rauhfutter') ~ 'grassland'))
cropcatnms = unique(fin$cropcat)
```

## Manipulate data and visualize
A first look at the distribution of yield per crop was useful to sort out minor crops. Additionally our categorization was checked regarding the distribution of the average yield of all included crops of each category. 

```{r overview crops}
# average yield per crop
mn_crop = fin %>% 
  group_by(crop,cropcat) %>%
  summarise(mn_dt = mean(dtha)) %>%
  arrange(cropcat)
# arrange plot for crop categories
Set2_12=colorRampPalette(brewer.pal(8,'Set2'))(12)
ggplot(mn_crop, aes(x=crop,y=mn_dt,  fill = cropcat)) + 
  geom_bar(stat = 'identity', width = 0.8) +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  ggtitle('Fig.1 Average yield of crops') +
  scale_fill_manual(values=Set2_12) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1)) 
ggplot(mn_crop, aes(x=cropcat,y=mn_dt,  fill = cropcat)) + 
  geom_bar(stat = 'identity', width = 0.8) +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  ggtitle('Fig.2 Average yield per crop category') +
  scale_fill_manual(values=Set2_12) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1), legend.position ='none')
```

The graphics show, that a cumulation of wheat, rye, oats to one group called cereals would be better comparable to other major crops. Other crop categories like legumes, rapeseed and sunflower can be disregarded due to low yield and unsuitable assignment to other categories.

```{r categorize 2}
fin = fin %>%
  mutate(cropcat2 = case_when(cropcat %in% c('cereal','wheat','rye','barley','oat') ~ 'cereal',
                              cropcat %in% c('legumes','rapeseed','sunflower','grassland') ~ 'other',
                              TRUE ~ cropcat))
cropcatnms2 = na.omit(unique(fin$cropcat2))
```

```{r overview year}
# average yield per year
mn_jahr = fin %>%
  group_by(year,cropcat2) %>%
  summarise(mn_dt = mean(dtha))

ggplot(mn_jahr, aes(x=year,y=mn_dt, fill=cropcat2)) + 
  geom_bar(position='stack', stat = 'identity', width =0.8) +
  labs(fill = 'crop category', y = 'dt/ha', x = 'year') +
  ggtitle('Fig.3 Average yield per year per crop category') +
  scale_fill_brewer(palette='Set2')+
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1))
# average yield per crop per year
mn_cropjahr = fin %>%
  group_by(year, crop, cropcat, cropcat2) %>%
  summarise(mn_dt = mean(dtha))
bigcrop = filter(mn_cropjahr,mn_dt>100)
smallcrop = filter(mn_cropjahr,mn_dt<100)

unique(bigcrop$crop)
cropjahrlegend = c('potatoes','early year potatoes', 'late year potatoes','sugar beet','fodder beet','silage maize')
ggplot() +
  geom_point(aes(x=year, y=mn_dt, colour = crop), bigcrop) +
  geom_line(aes(x=year, y=mn_dt,group = crop, colour = crop), bigcrop) +
  geom_point(aes(x=year, y=mn_dt), smallcrop, colour='grey50') +
  geom_line(aes(x=year, y=mn_dt,group = crop), smallcrop, colour='grey50') +
  labs(y = 'dt/ha', x = 'year') +
  ggtitle('Fig.4 Average yield of crops for each year from 2005 to 2015') +
  scale_colour_manual(name  ='crop', values=c('#CC0000','#CC6600','#FFFF00','#00CCCC','#0066CC','#0000CC'),
                      labels=cropjahrlegend) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 0.5))
#Average of the total crop yield per year for 2005 to 2009
cropyearspan1 = fin %>%
  filter(year<2010) %>%
  group_by(year,gen) %>%
  summarise(sum_dt=sum(dtha)) %>%
  ungroup() %>%
  group_by(gen) %>%
  summarise(mn_dt=mean(sum_dt))
#Average of the total crop yield per year for 2010 to 2015
cropyearspan2 = fin %>%
  filter(year>=2010) %>%
  group_by(year,gen) %>%
  summarise(sum_dt=sum(dtha)) %>%
  ungroup() %>%
  group_by(gen) %>%
  summarise(mn_dt=mean(sum_dt))
#map for years 2005 to 2009
summary(cropyearspan1)
tm_yearspan1 = tm_shape(cropyearspan1) + 
  tm_polygons('mn_dt', palette='Blues', breaks=c(0,1000,2000,3000,4000,5000), id='dt/ha', title='dt/ha') +
  tm_compass() + 
  tm_scale_bar() + 
  tm_layout('Fig.5 Average over years 2005 to 2009 of total yield', title.bg.color = 'white')
#map for years 2010 to 2015
tm_yearspan2 = tm_shape(cropyearspan2) + 
  tm_polygons('mn_dt', palette='Blues', breaks=c(0,1000,2000,3000,4000,5000), id='dt/ha', title='dt/ha') +
  tm_compass() + 
  tm_scale_bar() + 
  tm_layout('Fig.6 Average over years 2010 to 2015 of total yield', title.bg.color = 'white')
#map plotting
tmap_arrange(tm_yearspan1, tm_yearspan2)
```

The graph in figure 4 shows, that some previously largely harvested crops fell significantly in yield below the 100 dt per ha mark in 2007 and 2009. This either indicates corrupted data, deviating data acquisition forms or actual drop of yield for those  specific crops. One possible reason could be the EU's energy crop directive of 2009 (EU2009 --> Official Journal of the European Union, https://eur-lex.europa.eu/LexUriServ/LexUriServ.do?uri=OJ:L:2009:140:0016:0062:EN:PDF)
Therefore the final dataframe was refined to only include data of years after 2009.

To have a glimpse over the geogrpahical distribution of yield districtwise we plotted a map-visual approach and a facet-barplot approach. We used the abbreviations of districts for license plates to shorten the district names for plots. The assignment code can be found below (dataframe 'abbcode').

```{r crops of district}
#abbreviation of districts
fin = fin %>%
  mutate(gn = plyr::mapvalues(gen, 
            from= unique(fin$gen), 
            to=c('D','DU','E','KR','MG','MH','OB','RS','SG','W','KLE','ME','NE','VIE','WES','BN','K','LEV','AC','DN','BM','EU','HS','GM','GL','SU','BOT','GE','MS','BOR','COE','RE','ST','WAF','BI','GT','HF','HX','LIP','MI', 'PB', 'BO','DO','HA','HAM','HER','EN','HSK','LS','OE','SI','SO','UN')))
abbcode = data.frame(gen = unique(fin$gen), gn = unique(fin$gn))
abbcode
# facetting approach for yield per crop per district barplot
cropkreis = fin %>%
  #filter years 2009 and before
  filter(year>=2010) %>%
  #calculate average yield per crop per district over the 5 years
  group_by(crop,cropcat2,gen,gn) %>%
  summarise(mn_dt = mean(dtha)) %>%
  ungroup() %>%
  #calculate sum of yield per crop category per district
  group_by(cropcat2,gen,gn) %>%
  summarise(sum_dt = sum(mn_dt))

ggplot(cropkreis, aes(x=cropcat2, y=sum_dt, fill = cropcat2))+
  geom_bar(stat='identity') +
  facet_wrap(~gn, ncol = 10) +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  ggtitle('Fig.7 Average yield per crop category for each district') + 
  scale_fill_brewer(palette='RdYlBu') +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_text(size = 7))
```

```{r crop index}
ci = fin %>%
  #filter years 2009 and before
  filter(year>=2010) %>%
  #calculate average yield per crop per district over the 5 years
  group_by(crop,cropcat2,gen,gn) %>%
  summarise(mn_dt = mean(dtha)) %>%
  ungroup() %>%
  #calculate sum of yield per district 
  group_by(cropcat2,gen,gn) %>%
  summarise(sum_dt = sum(mn_dt)) %>%
  #add column for total crop yield per district
  group_by(gn) %>%
  mutate(totsum_dt = sum(sum_dt))


tm_compass()+
tm_scale_bar()+
  tm_shape(ci) +
  tm_fill('totsum_dt', style='pretty', palette='Blues', textNA='district yield below average', title='total yield in dt/ha') +
  tm_symbols(size = 'sum_dt', scale=3, col ='cropcat2',palette='Set2', alpha=1, border.lwd=0.1,border.alpha=0.5, 
             title.size ='sum of yield in dt/ha', title.col = 'crop category', title.shape='') +
tm_shape(nrw) +
  tm_borders() +
tm_layout(main.title='Fig.9 Crop index', title.snap.to.legend =TRUE, legend.outside = TRUE, legend.outside.position='right')
```

## Merge with pesticide data

To compare the crop yield with the pesticide usage, the sum of pesticide sample values were calculated for each district.

```{r data-spatial-pesticides}
nrw2 = readRDS(file.path('data/nrw', 'nrw_sites.rds')) # spatial sites data
nrw_sam = readRDS(file.path('data/nrw', 'nrw_samples.rds')) # pesticide samples
nrw_sam$site_id = gsub('_....-..-..','',nrw_sam$sample_id) #create site_id in sample data.frame to merge by
pestnofilter = merge(nrw2, nrw_sam, by='site_id')
# sort out values below loq and with NAs with value_fin
pest = pestnofilter %>%
  filter(value_fin>0)
#visualize all samples and sites
tmap_options(max.categories=48)
tm_compass()+
tm_scale_bar()+
  tm_shape(ci) +
  tm_fill('totsum_dt', style='pretty', palette='Blues', 
          textNA='district yield below average', title='total yield in dt/ha') +
tm_shape(nrw) +
  tm_borders() +
tm_shape(pest) +
  tm_symbols(size = 'value_fin', scale=3, col='psm_type' ,palette='Set2', alpha=0.8, border.alpha = 0.6, border.lwd=0.2, 
             title.size ='value of pesticide samples', title.col = 'type of pesticide', title.shape='') +
tm_layout(main.title='Fig.10 Pesticide samples and crop index', title.snap.to.legend =TRUE, legend.outside = TRUE, legend.outside.position='right')

pestindex = pest %>%
  select(site_id, area_sqkm, atkis_perc, name, cas, qualifier, value_fin, psm_type) %>%
  mutate(atkis_perc = atkis_perc*100) #agricultural proportion converted into percentage
# create sf object with sites and their agricult.prop. (atkis_perc)
atkischeck = pestindex %>%
  group_by(site_id) %>%
  summarise(atkis_perc = mean(atkis_perc)) %>%
  arrange(atkis_perc)
# intersect this sf object with the district sf object
# therefore transformation fitting to the german EPSG:31467
st_crs(atkischeck)
st_crs(nrw)
nrw = st_transform(nrw, crs = st_crs(atkischeck))
atkis_kreis = st_intersection(nrw, atkischeck)
# choose site with highest agricul.prop. per district
atkis_kreis = atkis_kreis %>%
  #for each district calculate the maximal value of agricul.prop.
  group_by(rs) %>%
  mutate(max_atkis = max(atkis_perc)) %>%
  # summarise only the site_ids of which their agricul.prop. equals the max agricul.prop.
  summarise(bestsite = na.omit(case_when(atkis_perc==max_atkis ~ site_id,
                                         TRUE ~ NA_character_)))
#save a vector with those site_ids
#since the geometries of the polygons of catchment areas overlap the districts, there are some sites referenced by multiple districts
bestsites = unique(atkis_kreis$bestsite)
length(bestsites)       #check how many sites exist (one site per district was chosen, if available)
length(unique(nrw$rs))  #check how many districts exist
# filter original pest sf_object for the best sites
pestindex = pestindex %>%
  filter(case_when(site_id %in% bestsites ~ TRUE,
                   TRUE ~ FALSE))
#to compare the districts we choose 
pestindexdt = as.data.table(pestindex)
counts = pestindexdt[, .(rowCount =.N), by = c('cas','name','psm_type')]
counts = setorder(counts, rowCount)
tail(counts,n=16)
#choose three herbicides  and an insecticide and an fungicide of which the most samples exist
# herbicides 	93-65-2             Mecoprop
#             330-54-1            Diuron
#             34123-59-6          Isoproturon
# insecticide 534-52-1            4,6-Dinitro-o-Cresol
# fungicide   133855-98-8         Epoxiconazol
pestindex = pestindex %>%
  filter(cas %in% c('93-65-2','330-54-1','34123-59-6','534-52-1','133855-98-8'))
#merge the cropindex and pestindex
st_crs(pestindex)
st_crs(ci)
ci=st_transform(ci,crs=st_crs(pestindex))
pestcrop = st_intersection(ci,pestindex)
pestcrop %>% group_by(name) %>% summarise(max(value_fin))
pestcrop = pestcrop %>%
  mutate(concindex = case_when(name=='Mecoprop' ~ value_fin*20,
                               name=='Diuron' ~ value_fin*5,
                               name=='4,6-Dinitro-o-Cresol' ~ value_fin*20,
                               name=='Epoxiconazol'~ value_fin*40,
                               name=='Isoproturon'~value_fin))
pestcrop %>% group_by(name) %>% summarise(max(concindex))
#plot the use of pesticides per district
ggplot(pestcrop)+
  geom_bar(stat='identity', aes(x=name, y=concindex, fill = psm_type)) +
  facet_wrap(~gn, ncol = 10) +
  labs(fill = 'pesticide', y = 'concentration index', x = '') +
  ggtitle('Fig.11 Pesticide index of 5 pesticides ') + 
  scale_fill_brewer(palette='Set2') +
  theme(axis.text.x=element_text(angle=90, size =7),axis.text.y = element_text(size = 7))
```
