---
title: 'Crop data'
output: html_document
editor_options: 
  chunk_output_type: console
---

## Packages
test
```{r packages}
require(data.table)
require(sf)
require(mapview)
require(stringr)
require(plyr)
require(dplyr)
require(ggplot2)
require(forcats)
require(tidyr)
require(tmap)
require(grid)
require(gridExtra)
require(RColorBrewer)
require(funchir) #delete after checking which packages are unused with stale_package_check('crop.Rmd')
```

## Harvest data
(1) A list named fl_vec of every name of the datatables in the data/nrw directory was created 
(2) A new list named l was created
(3-5) Every table from the data named as the strings in the list fl_vec was implemented in a dataframe named dat
(6) The first row  was dropped, but why?
(7) The names for the first two columns representing the district number and the district name were set to 'rs' and 'gen'
(8) The list l was filled with the rows, each containing a dataframe from dat for every year
(9) the names of the rows in l are reduced from the data name to only the yearnumber
(10) rbindlist stacked all the data.frames of the list l to a single data.frame and labeled the id column to year

```{r data-harvest}
# read list of files
fl_vec = list.files('data/nrw', pattern = 'csv', full.names = TRUE)
l = list()
for (i in seq_along(fl_vec)) {
  fl = fl_vec[i]
  dat = fread(fl, skip = 7, header = TRUE, encoding = 'Latin-1', stringsAsFactors = FALSE)
  dat = dat[-1, ]
  setnames(dat, 1:2, c('rs', 'gen'))
  
  l[[i]] = dat
  names(l)[i] = gsub('ernte|.csv', '', basename(fl))
}
# bind list of data.table to one data.table
dt = rbindlist(l, fill = TRUE, idcol = 'year')

# remove special symbols and convert column types to numeric
dtc = data.frame(dt)
for(i in 4:41){
  dtc[,i] =  gsub('[-.x]','0',dtc[,i])
  dtc[,i] = gsub('[,]','.',dtc[,i])
}
for(i in 4:41){
  dtc[,i] = as.numeric(dtc[,i])
}
# bring data into long format (year, rs, gen as identifier variables)
crop_names = colnames(dtc[,4:41])
setDT(dtc)
str(dtc)
dtc_long = melt(dtc, id.vars = c('year','rs','gen'), measure.vars = crop_names, variable.name = 'crop', value.name = 'dtha' )
```

(1) Shapefiles der Kreise Deutschlands werden eingelesen.
(2) Namen der Spalten werden alle nun klein geschrieben
(3) rs der Kreise soll als numeric typisiert sein --> merge mit rs aus dtc
(4) kreis2 ist Tabelle aus Kopie der Spalten rs, rs_alt, ... von kreis
(5) zeigt die Karte an

```{r data-spatial-regions}
kreis = st_read(file.path('data', 'germany_kreis.shp'), stringsAsFactors = FALSE)
setnames(kreis, tolower(names(kreis)))
kreis$rs = as.numeric(kreis$rs)
kreis2 = kreis[ , names(kreis) %in% c('rs', 'rs_alt', 'geom', 'shape_leng', 'shape_area') ]
# refine to NRW only
kreis3 = kreis2[0,]
for (i in 1:402){
  if (kreis2$rs[i]>5000 & kreis2$rs[i]<6000){
    rbind(kreis3)
  kreis3[nrow(kreis3)+1,] = kreis2[i,]
  }
}
#nrw as a whole geometry for visualization purposes
mapview(kreis3)
nrw = st_union(st_geometry(kreis3))
```

To organize the data, the crops were renamed and categorized in another column into 11 factors.

```{r merge and categorize}
# merge geo and crop data
fin = merge(kreis3, dtc_long)
# shorten crop names
cropnms = gsub('[.]', ' ', crop_names)
cropnms[1] = 'GetreidemitCCM'
cropnms[2] = 'GetreideohneCCM'
cropnms[7] = 'Hartweizen'
cropnms[8] = 'Roggenmit'
cropnms[11] = 'Futtergetreide'
cropnms[10] = 'Wintergetreide'
cropnms[16] = 'Sommergetreide'
cropnms[18] = 'KörnermaismitCCM'
cropnms[21] = 'Spätkartoffeln'
cropnms[24] = 'Leguminosen'
cropnms[25] = 'Erbsen'
cropnms[28] = 'Sommerraps'
cropnms[31] = 'Getreideganz'
cropnms[33] = 'Weiden'
cropnms[34] = 'Feldgras'
cropnms[35] = 'KleeLuzerne'
cropnms[37] = 'Silomais'
# rename crops
fin$crop = mapvalues(fin$crop, from = crop_names, to = cropnms)
# categorize crops
fin = fin %>%
  mutate(cropcat = plyr::mapvalues(crop, 
            from= c('GetreidemitCCM','GetreideohneCCM','Brotgetreidearten','Wintergetreide','Futtergetreide','Sommergetreide','Triticale'), 
            to= c('cereal','cereal','cereal','cereal','cereal','cereal','cereal'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Winterweizen','Sommerweizen','Getreideganz','Hartweizen','Weizen'), 
            to= c('wheat','wheat','wheat','wheat','wheat'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Roggenmit','Roggen'), 
            to=c('rye','rye'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Gerste','Wintergerste','Sommergerste'), 
            to= c('barley','barley','barley'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Hafer'), 
            to= c('oat'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('KörnermaismitCCM','Silomais'),
            to= c('maize','maize'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Frühkartoffeln','Kartoffeln','Spätkartoffeln'),
            to= c('potatoes','potatoes','potatoes'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Zuckerrüben','Runkelrüben'),
            to= c('beets','beets')))%>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Winterraps','Sommerraps','Sonnenblumen'),
            to= c('RapeseedSunflower','RapeseedSunflower','RapeseedSunflower'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Leguminosen','Erbsen','Ackerbohnen','KleeLuzerne','Luzerne','Süßlupinen'),
            to= c('legumes','legumes','legumes','legumes','legumes','legumes'))) %>%
  mutate(cropcat = plyr::mapvalues(cropcat, 
            from= c('Wiesen','Weiden','Feldgras','Rauhfutter'),
            to= c('grassland','grassland','grassland','grassland')))
cropcatnms = unique(fin$cropcat)
```

## Manipulate data and visualize
A first look at the distribution of yield per crop was useful to sort out minor crops. Additionally our categorization was checked regarding the distribution of the average yield of all included crops of each category. 

```{r overview crops}
# average yield per crop
mn_crop = fin %>% 
  group_by(crop,cropcat) %>%
  summarise(mn_dt = mean(dtha)) %>%
  arrange(cropcat)

# TODO arrange plot for crop categories HOW?
ggplot(mn_crop, aes(x=crop,y=mn_dt,  fill = cropcat)) + 
  geom_bar(stat = 'identity', width = 0.8) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1)) +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  scale_fill_brewer(palette='RdYlBu') +
  ggtitle('Fig.1 Average yield of crops')

ggplot(mn_crop, aes(x=cropcat,y=mn_dt,  fill = cropcat)) + 
  geom_bar(stat = 'identity', width = 0.8) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1), legend.position ='none') +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  scale_fill_brewer(palette='RdYlBu') +
  ggtitle('Fig.2 Average yield per crop category')
```

The graphics show, that a cumulation of wheat, rye, oats to one group called cereals would be better comparable to other major crops. Other crop categories like legumes, rapeseed and sunflower can be disregarded due to low yield and unsuitable assignment to other categories.

```{r categorize 2}
fin = fin %>%
  mutate(cropcat2 = plyr::mapvalues(cropcat, 
            from= c('cereal','wheat','rye','barley','oat'), 
            to= c('cereals','cereals','cereals','cereals','cereals'))) %>%
  mutate(cropcat2 = plyr::mapvalues(cropcat2, 
            from= c('legumes','RapeseedSunflower','grassland'), 
            to= c(NA,NA,NA)))
# refine data for final cropindex cropwise
cropindex = fin %>%
  na.omit()
cropcatnms2 = na.omit(unique(fin$cropcat2))
```

```{r overview year}
# average yield per year
mn_jahr = fin %>%
  group_by(year,cropcat2) %>%
  summarise(mn_dt = mean(dtha))

ggplot(mn_jahr, aes(x=year,y=mn_dt, fill=cropcat2)) + 
  geom_bar(position='stack', stat = 'identity', width =0.8) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 1, hjust = 1)) +
  ggtitle('Fig.3 Average yield per year')

# average yield per crop per year
# TODO have both colour codings in legend
mn_cropjahr = fin %>%
  group_by(year, crop, cropcat, cropcat2) %>%
  summarise(mn_dt = mean(dtha))
bigcrop = filter(mn_cropjahr,mn_dt>100)
smallcrop = filter(mn_cropjahr,mn_dt<100)

cropjahrlegend = cbind(unique(bigcrop$crop),c('other'))
ggplot() +
  geom_point(aes(x=year, y=mn_dt, colour = crop), bigcrop) +
  geom_line(aes(x=year, y=mn_dt,group = crop, colour = crop), bigcrop) +
  geom_point(aes(x=year, y=mn_dt), smallcrop, colour='grey50') +
  geom_line(aes(x=year, y=mn_dt,group = crop), smallcrop, colour='grey50') +
  ggtitle('Fig.4 Average yield of crops for each year from 2005 to 2015') +
  scale_colour_manual(name  ='crop', values=c('#CC0000','#CC6600','#FFFF00','#00CCCC','#0066CC','#0000CC'), labels=cropjahrlegend) +
  theme(axis.text.x = element_text(angle = 45, size = 9, vjust = 0))

#crop yield for the three yearspans mapped to districts
cropyearspan1 = fin %>%
  filter(year<2010) %>%
  group_by(gen) %>%
  summarise(mn_dt=mean(dtha))
cropyearspan2 = fin %>%
  filter(year>=2010) %>%
  group_by(gen) %>%
  summarise(mn_dt=mean(dtha))
tm_compass() + tm_scale_bar() + tm_shape(cropyearspan1) + tm_sf('mn_dt', palette='RdYlBu', breaks = c(0,30,60,90,120,150,180), id='dt/ha', title='dt/ha')  + tm_shape(nrw) + tm_borders(lwd = 2, col='grey30')+ tm_layout(title='Fig.5 Average yield per district from 2005 to 2009', title.bg.color=TRUE)
tm_compass() + tm_scale_bar() + tm_shape(cropyearspan2) + tm_sf('mn_dt', palette='RdYlBu', breaks = c(0,30,60,90,120,150,180), id='dt/ha', title='dt/ha')  + tm_shape(nrw) + tm_borders(lwd = 2, col='grey30')+ tm_layout(title='Fig.6 Average yield per district from 2010 to 2015', title.bg.color=TRUE)

#refine dataframe to exclude data before 2009
cropindex = cropindex %>%
  filter(year>=2010)
```

The graph in figure 4 shows, that some previously largely harvested crops fell significantly in yield below the 100 dt per ha mark in 2007 and 2009. This either indicates corrupted data, deviating data acquisition forms or actual drop of yield for those  specific crops. One possible reason could be the EU's energy crop directive of 2009 (EU2009 --> Official Journal of the European Union, https://eur-lex.europa.eu/LexUriServ/LexUriServ.do?uri=OJ:L:2009:140:0016:0062:EN:PDF)
Therefore the dataframe was refined to only include data of years after 2009.

To have a glimpse over the geogrpahical distribution of yield districtwise we plotted a map-visual approach and a facet-barplot approach. We used the abbreviations of districts for license plates to shorten the district names for plots. The assignment code can be found below (dataframe 'abbcode').

```{r crops of district}
#abbreviation of districts
fin = fin %>%
  mutate(gn = plyr::mapvalues(gen, 
            from= unique(fin$gen), 
            to=c('D','DU','E','KR','MG','MH','OB','RS','SG','W','KLE','ME','NE','VIE','WES','BN','K','LEV','AC','DN','BM','EU','HS','GM','GL','SU','BOT','GE','MS','BOR','COE','RE','ST','WAF','BI','GT','HF','HX','LIP','MI', 'PB', 'BO','DO','HA','HAM','HER','EN','HSK','LS','OE','SI','SO','UN')))
abbcode = data.frame(gen = unique(fin$gen), gn = unique(fin$gn))
abbcode

# average yield of each categorized crops per district
# l = list()
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# for (i in 1:length(cropcatnms)){
# mn_cropkreis = fin %>%
#   group_by(cropcat,gen) %>%
#   summarise(mn_dt = mean(dtha)) %>%
#   filter(cropcat == cropcatnms[i])
#   l[[i]] =  ggplot(data = mn_cropkreis) +
#   geom_sf(aes(fill = mn_dt)) + 
#     scale_fill_gradientn(colours = myPalette(100), limits=c(0,800)) +
#   ggtitle(cropcatnms[i])#, subtitle = 'yield in dt per ha')
#   if(i==length(cropcatnms)){ 
#     l[[i]] = l[[i]] + theme(axis.text = element_blank(), axis.ticks = element_blank())
#   }
#   else {
#     l[[i]] = l[[i]] + theme(axis.text = element_blank(), axis.ticks = element_blank(), legend.position = 'none')
#   }
# }
# do.call(grid.arrange, c(l, top='Fig.5 Average yield of each crop category mapped for each district'))

#TODO get tm_facets working
mn_cropkreis = fin %>%
  na.omit() %>%
  group_by(cropcat2, gen, gn) %>%
  summarise(mn_dt = mean(dtha)) 

tm_layout(title='Fig.7 Average yield per district per crop category', title.bg.color=TRUE) +
  tm_shape(nrw) + 
  tm_borders(lwd = 2, col='grey30')+ 
  tm_compass() + tm_scale_bar() + 
tm_shape(mn_cropkreis) + 
  tm_sf('mn_dt', palette='RdYlBu') + 
  tm_facets(by='cropcat2')

# facetting approach for yield per crop per district barplot
#TODO show with visual effect (red border, ..) which districts get sorted out
mn_cropkreisf = fin %>%
  na.omit() %>%
  group_by(cropcat2,gn) %>%
  summarise(mn_dt = mean(dtha))
ggplot(mn_cropkreisf, aes(x=cropcat2, y=mn_dt, fill = cropcat2))+
  geom_bar(stat='identity') +
  facet_wrap(~gn, ncol = 10) +
  labs(fill = 'crop category', y = 'dt/ha', x = '') +
  scale_fill_brewer(palette='RdYlBu') +
  ggtitle('Fig.8 Average yield per crop category for each district') + 
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_text(size = 7))

#add abbreviation and sort out districts of low agriculture
cropindex = cropindex %>%
  mutate(gn = plyr::mapvalues(gen, 
            from= unique(fin$gen), 
            to=c('D','DU','E','KR','MG','MH','OB','RS','SG','W','KLE','ME','NE','VIE','WES','BN','K','LEV','AC','DN','BM','EU','HS','GM','GL','SU','BOT','GE','MS','BOR','COE','RE','ST','WAF','BI','GT','HF','HX','LIP','MI', 'PB', 'BO','DO','HA','HAM','HER','EN','HSK','LS','OE','SI','SO','UN'))) %>%
  group_by(gn) %>%
  filter(summarise(sum_dtha = sum(mn_dt))>500)
```

```{r crop index}
# TODO Auswahl der Kategorien und Berechnung eines Index

```

## Merge with pesticide data

To compare the crop yield with the pesticide usage, the sum of pesticide sample values were calculated for each district.

```{r data-spatial-pesticides}
nrw2 = readRDS(file.path('data/nrw', 'nrw_sites.rds')) # spatial sites data
nrw_sam = readRDS(file.path('data/nrw', 'nrw_samples.rds')) # pesticide samples
nrw_sam$site_id = gsub('_....-..-..','',nrw_sam$sample_id)
pest = merge(nrw2, nrw_sam)
#Transformation fitting to german EPSG: and Intersection 
st_crs(pest)
st_crs(cropindex)
mn_kreis = st_transform(cropindex, crs = st_crs(pest)) 
# geometrische Koordsysteme besser für 2dimensionale GIS Arbeiten heißt 31467 praktischer
pestcrop = st_intersection(cropindex, pest) #insert crop index dataframe here

#TODO barplot Pestizide mit höchsten Konzentrationen

#TODO calculate pest index - Messstation mit höchstem Landwirtschaftsanteil
 
#TODO visualize

```

## Tasks

- Part1:
  - Clean crop data
  - Merge with spatial data
  - Aggregate crop data
  - Select 5-10 regions (i.e. Kreis) with the most agriculture
  - Visualize regions with intensive agriculture

- Part2:
  - Intersect with pesticide sampling sites
  - Look if sites with high concentrations intersect well with regions (i.e. Kreis) with high agriculture
  - Visualize this

- Document this in R-Markdown
- Presentation?


